Arc Blanc: a real time ocean simulation framework

### 2025-01-29 paper.tex
Clarify the volume computation and the assumptions that were made on the vessels

%-------------------------------------------------------------------------
\section{Fluid-to-solid action}
\label{sec:fluidToSolidAction}
The action of the fluid on a given solid can be approximated by a \emph{set of forces} acting continuously on the \emph{contact surface} between the fluid and the solid.
In \framework, the contact surface is represented using the triangulation of the solid's mesh, leading to a discrete approximation of the set of forces.
Moreover, to remain real-time \framework uses forces computed from simple geometric and physical parameters only.

@@

The buoyancy calculation presented in Section \ref{subsubsec:buoyancy} requires the full submerged volume $v_w$ of the mesh.
\Framework uses the prism approximation proposed by Bajo \etal (2020) \cite{bajoRealisticBuoyancyModel2020a}.
The principles of their method are as follows: from each submerged triangle $T_i^s$ of the body, a prism is build up to the water surface; hence, each prism volume can be calculated, and so the full submerged volume $v_w$ by adding all of them.

>>>>

%-------------------------------------------------------------------------
\section{Fluid-to-solid action}
\label{sec:fluidToSolidAction}
The action of the fluid on a given solid can be approximated by a \emph{set of forces} acting continuously on the \emph{contact surface} between the fluid and the solid.
In \framework, the contact surface is represented using the triangulation of the solid's mesh, leading to a discrete approximation of the set of forces.
Moreover, to remain real-time \framework uses forces computed from simple geometric and physical parameters only.
To maintain realistic physics after these discrete approximations and those described in subsequent sections, it is important to use a closed mesh, uniformly triangulated. In addition, for meshes representing vessels, ensuring symmetry is crucial to maintain stability.

@@

The buoyancy calculation presented in Section \ref{subsubsec:buoyancy} requires the full submerged volume $v_w$ of the mesh.
\Framework uses the prism approximation similarly to the approximation proposed by Bajo \etal (2020) \cite{bajoRealisticBuoyancyModel2020a}. 
While Bajo \etal compute the submerged volume at the texel level, the same principle can be applied using triangles instead of texels using as they did the divergence theorem. 
Specifically, $v_w$ is approximated as the sum of the prisms with bases corresponding to the triangle areas $A_i$ and heights defined by the distance between the triangle centers $p_i$ and the water surface $h(x,z,t)$. 
Each term in the sum is weighted by the vertical component of the triangle normal $n_i^y$:
\begin{equation}
v_w = \sum_{T_i^s} (h(x,z,t) - p_i) A_i n_i^y.
\end{equation}
Note that this formula is correct only under the assumption that the mesh is closed.
